---
title: "lab3"
author: "Marisol"
date: "26/02/2021"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Data

Today, we’ll use ggplot to visually explore global trends in public health and economics compiled by the Gapminder project. This project was pioneered by Hans Rosling, who is famous for describing the prosperity of nations over time through famines, wars and other historic events with this beautiful data visualization in his 2006 TED Talk: The best stats you’ve ever seen:



```{r}

library(dslabs)
library(tidyverse)

gap2011 <- gapminder %>% 
  as_tibble() %>% 
  filter(year == 2011)

```

## Life expectancy

How does life expectancy vary by continent in the year 2011? 

```{r}

ggplot(gap2011, aes(x = continent, y = life_expectancy, color = continent)) + geom_boxplot()


```

How does life expectancy relate to infant mortality rate? 


```{r}

ggplot(gap2011, aes(x = infant_mortality, y = life_expectancy,color = continent)) + geom_point()


```


## Fertility

## Infant mortality




